\subsection{Task Scheduling Project}

This project is a practical exploration of task scheduling in FreeRTOS. It involves two tasks, each of which prints a message to the console. The priority of these tasks and the preemption setting of the scheduler can be adjusted to observe different behaviors.

\subsubsection{Project Initialization and Execution}

The project is initialized with two tasks of equal priority. Each task prints a message ("Hello from Task x") to the console every second, thanks to a \textbf{delay} added to each task. The scheduler is set to \textbf{preemptive} mode, which means that it can interrupt a currently running task to start executing a higher-priority task.

When the project runs, the console output shows that each task is executed in a \textbf{round-robin} way, as expected in a preemptive scheduler with tasks of equal priority in FreeRTOS.

\subsubsection{Disabling Preemption}

When preemption is disabled, the scheduler cannot interrupt a running task until it has finished. The expected behavior is that the first task runs indefinitely, and the second task is never executed. Though we observe the same behavior as in the preemptive mode.

The reason for this is that each task includes a delay using the \texttt{vTaskDelay} function, which put the task in the \textbf{blocked} state for a specified period. This allows the other task to be executed, despite the lack of preemption.

If the delay is removed from both tasks and preemption is disabled, the first task runs indefinitely, and the second task is never executed.

\subsubsection{Changing Task Priorities}

If the priority of Task 2 is set higher than that of Task 1, then when the project is run, Task 2 is executed indefinitely, and Task 1 is never executed. This is because the scheduler always chooses the highest-priority task to run.

Even if preemption is re-enabled, the output does not change, because Task 2 still has a higher priority than Task 1. The scheduler will always choose Task 2 over Task 1, regardless of whether it can preempt the currently running task.